---
title: "Homework: Reproducibility and Professional Communication"
execute:
  error: true
author: "Sukainah "
output: html_document

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
options(digits = 3)
```


# Reproducible Examples & Debugging

In the following examples, evaluate each problem using the criteria of a minimal reproducible example from [this StackOverflow post](https://stackoverflow.com/help/minimal-reproducible-example). 

Specifically, address the following things: 

1. Are the question and problem description complete?

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

3. Is the example minimal? Does it include extra code or information that is not necessary?

4. Does the question describe any attempted solutions?


Then, using what you know about R and Python, try to debug the problem using the strategies in [the debugging chapter](https://srvanderplas.github.io/stat-computing-r-python/part-gen-prog/06-debugging.html). Once you are thoroughly stumped, or you believe you have solved the problem, compare your solutions to those given on StackOverflow using the link.

## Why Doesn't this R function work?

> I created the following function to append new strings on a vector of strings called "meals". However, when I use this function to append an string input into my "meals" vector, it does not work.

```
 add <- function(str) {
      meals <- append(meals, as.character(str))  
    }
```

[Link](https://stackoverflow.com/questions/39795961/why-doesnt-this-r-function-work?noredirect=1&lq=1) to original SO post. 


---

1. Are the question and problem description complete?

its seems complete, the question is trying to append string to a vector meals 

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

yes ,reproducible,where the code show us the function,but I cant see how meals initilized.
to improve it we need to include example shows initializing 


3. Is the example minimal? Does it include extra code or information that is not necessary?

there is no extra code so yes,its minimal .

4. Does the question describe any attempted solutions?
I cant see any debugging attempts, or any corrections.
the code create function with local copy of meals ,but we dont have the vector meals so now I will try to add this vector and run the code 


```{r}
# define meals vector 
meals<-c("veggy","meditarian")
add <- function(str, meals) {
  return(append(meals, as.character(str)))
}
#add other meal type to the vector 
meals <- add("diet", meals)
#check my results
print(meals)


```



## Function not working R

> I've never programmed before and am trying to learn. I'm following that "coursera" course that I've seen other people post about — a course offered by Johns Hopkins on R programming.

> Anyway, this was supposed to be my first function. Yet, it doesn't work! But when I type out all the steps individually, it runs just fine... Can anyone tell me why?

```
pollutantmean <- function(directory, pollutant, id = 1:332){
    x<- list.files("/Users/mike******/Desktop/directory", full.names=TRUE)
    y<- lapply(x, read.csv)
    z<- do.call(rbind.data.frame, y[id])

    mean(z$pollutant, na.rm=TRUE)
}
pollutantmean(specdata,nitrate,1:10)
[1] NA
Warning message:
In mean.default(z$pollutant, na.rm = TRUE) :
  argument is not numeric or logical: returning NA

####

x<- list.files("/Users/mike******/Desktop/specdata",full.names=TRUE)
y<- lapply(x,read.csv)
z<- do.call(rbind.data.frame,y[1:10])
mean(z$nitrate,na.rm=TRUE)
[1] 0.7976266
```


[Link](https://stackoverflow.com/questions/24123224/function-not-working-r/24141502)


---

1. Are the question and problem description complete?
I can the error message and the working code parts, and also mention that they follow coursera course.
so yes I can say complete.

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?
I dont have the file path to run the code exactly , but the error message explain the logice issue.
I think the best thing to improve is to built data set ,

3. Is the example minimal? Does it include extra code or information that is not necessary?
minimal, though the personal file path cant be generated,but still comparing with working manual code will help us




4. Does the question describe any attempted solutions?
yes, it mentioned than when trype steps indivdually ,it works, which help us ,
```{r}

pollutantmean <- function(directory, pollutant, id = 1:332){
    x <- list.files(directory, full.names=TRUE)  # Use parameter, not hardcoded path
    y <- lapply(x, read.csv)
    z <- do.call(rbind.data.frame, y[id])
    mean(z[[pollutant]], na.rm=TRUE)  # Use [[ ]] instead of $
}
```



## Inexplicable error when trying to export my R notebook

> Getting this error from R Markdown when trying to export my .RMD

```
"Error in filter(Gastropods, Species == "Cellana") :  object 'Species' not found Calls: <Anonymous> ... withCallingHandlers -> withVisible -> eval -> eval -> filter"
```

> However, all my plots are coming out successfully. I can clearly see in the data that the species column is there and that Cellana is a species. No spelling errors or anything.

> My first 20 or so lines of code are below (between the ### symbols)


````{r echo=FALSE}
cat(paste(readLines("https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt"), collapse = '\n'))
````

You can find this sample file [here](https://raw.githubusercontent.com/unl-statistics/stat850/refs/heads/main/homework/debugging_3.txt)


[Link](https://stackoverflow.com/questions/44193367/inexplicable-error-when-trying-to-export-my-r-notebook)

---

1. Are the question and problem description complete?

The question is not totally complete ,we dont see the the actual data and full context,the error message is given, but we cant see the actual data structure.

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

some parts are  reproducible,I can see the code but not the data.it could be improve  by including a sample of the data .

3. Is the example minimal? Does it include extra code or information that is not necessary

It includes more code than necessary for a minimal example. 


4. Does the question describe any attempted solutions?

the question mentions checking for spelling errors and verifying the column exists.

```{r}

```


## Python if elif else statement

> I'm trying to create a program with python that calculate the cost for shipping.

> However, I can't run the program to where it works properly.

> What ever my total is the same amount comes out as $6 for US and $8 for Canada. I can't seem to get pass that.

> Example:

```
total = raw_input('What is the total amount for your online shopping?')
country = raw_input('Shipping within the US or Canada?')

if country == "US":
    if total <= "50":
        print "Shipping Costs $6.00"
    elif total <= "100":
            print "Shipping Costs $9.00"
    elif total <= "150":
            print "Shipping Costs $12.00"
    else:
        print "FREE"

if country == "Canada":
    if total <= "50":
        print "Shipping Costs $8.00"
    elif total <= "100":
        print "Shipping Costs $12.00"
    elif total <= "150":
        print "Shipping Costs $15.00"
    else:
        print "FREE"
```


[Link](https://stackoverflow.com/questions/19371643/python-if-elif-else-statement)

---

1. Are the question and problem description complete?

I can see that  the question describes the problem whic is shipping costs arent calculating correctly and always show the lowest tier.

2. Is the issue reproducible? Does it have a description of the problem, with code that reproduces the problem? What could improve it?

I think yes, its reproducible. I can see the code is complete and the problem description is there
it can be improved  by showing example inputs and expected .

3. Is the example minimal? Does it include extra code or information that is not necessary?

 it's minimal ,it shows only the  conditional logic

4. Does the question describe any attempted solutions?

No they didt mention any debugging attempts or any  tried correction.


# Professional Communication

## Slides

Create a set of quarto slides in the file slides.qmd. 

Set two different output formats - for instance, reveal.js and beamer. 

In your slides:

- Introduce yourself and show a picture of yourself
- Provide basic biographical information: birthday, where you grew up
- Show a picture of your favorite animal
- Provide your favorite plot, generated in either R or python. (This can be one you've generated in this class). Ensure that the code does not show, but the plot does.
- Provide a link to your CV, which you will generate in the next part.

https://www.overleaf.com/read/ntpnzsbdshms#522273

Select a CV template that uses either LaTeX or Markdown:

- https://github.com/kazuyanagimoto/quarto-awesomecv-typst
- https://github.com/schochastics/quarto-cv
- https://www.overleaf.com/latex/templates/tagged/cv

Use the template to create a curriculum vitae that has your education, work experience, and any other sections you would like to include. Compile your CV and link to it in your slides. 
